Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-09-23 manuscript.Rmd
First fully working version of code for testing

---
title: "Different rules for binocular combination of luminance in cortical and subcortical pathways"
author: "Federico G. Segala, Aurelio Bruno, Alex R. Wade &  Daniel H. Baker"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document: default
  pdf_document:
    toc: no
  html_document: default
bibliography: references.bib
csl: elife.csl
---

@@

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires XGB of storage)
# 2 - average data across participants, do bootstrapping and modelling
# 3 - download all raw data and analyse (requires XGB of storage)

# reasonably compact code to check which packages are installed, install the missing ones, and activate all
packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'osfr','FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
rawdir <- 'local/rawdata/'
if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
matchdir <- 'local/Matching/'
if (!file.exists(matchdir)){dir.create(matchdir)}   # create a local directory to store matching data
TFdir <- 'local/TFdata/'
if (!file.exists(TFdir)){dir.create(TFdir)}   # create a local directory to store  data from the temporal frequency experiment
figdir <- 'local/Figures/'
if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
datadir <- 'local/Data/'
if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data

@@

         # if the tar file of this participant's data doesn't exist
         if (!file.exists(paste0(rawdir,'P',100+participant,'.tar'))){
           # download it from OSF

@@

hdata <- read.csv(paste0(EEGdir,'headerfile.csv'))

d <- dir(datadir,pattern='*summaryC.RData',full.names=TRUE)

@@

    temp <- tempmeansP[,cond,level]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmeansP[cond,level] <- mbs$meanamp
    cleanmeansPCI[1,cond,level] <- mbs$lowerCI
    cleanmeansPCI[2,cond,level] <- mbs$upperCI
    }

    temp <- tempmasksP[,cond,level]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh)

          mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmasksP[cond,level] <- mbs$meanamp
    cleanmasksPCI[1,cond,level] <- mbs$lowerCI
    cleanmasksPCI[2,cond,level] <- mbs$upperCI
}

      temp <- apply(tempmeansE[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmeansEav[cond,level] <- mbs$meanamp
    cleanmeansEavCI[1,cond,level] <- mbs$lowerCI
    cleanmeansEavCI[2,cond,level] <- mbs$upperCI
      }

temp <- apply(tempmasksE[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmasksEav[cond,level] <- mbs$meanamp
    cleanmasksEavCI[1,cond,level] <- mbs$lowerCI
    cleanmasksEavCI[2,cond,level] <- mbs$upperCI
        }

temp <- apply(tempmeansE2[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmeansE2av[cond,level] <- mbs$meanamp
    cleanmeansE2avCI[1,cond,level] <- mbs$lowerCI
    cleanmeansE2avCI[2,cond,level] <- mbs$upperCI
        }

      temp <- apply(tempmasksE2[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmasksE2av[cond,level] <- mbs$meanamp
    cleanmasksE2avCI[1,cond,level] <- mbs$lowerCI
    cleanmasksE2avCI[2,cond,level] <- mbs$upperCI
        }

@@

      temp <- tempmeansE[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmeansE[ch,cond,level] <- mbs$meanamp
    cleanmeansECI[1,ch,cond,level] <- mbs$lowerCI
    cleanmeansECI[2,ch,cond,level] <- mbs$upperCI
}

      temp <- tempmasksE[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmasksE[ch,cond,level] <- mbs$meanamp
    cleanmasksECI[1,ch,cond,level] <- mbs$lowerCI
    cleanmasksECI[2,ch,cond,level] <- mbs$upperCI
        }

      temp <- tempmeansE2[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmeansE2[ch,cond,level] <- mbs$meanamp
    cleanmeansE2CI[1,ch,cond,level] <- mbs$lowerCI
    cleanmeansE2CI[2,ch,cond,level] <- mbs$upperCI
        }

      temp <- tempmasksE2[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
    cleanmasksE2[ch,cond,level] <- mbs$meanamp
    cleanmasksE2CI[1,ch,cond,level] <- mbs$lowerCI
    cleanmasksE2CI[2,ch,cond,level] <- mbs$upperCI
        }

@@

meanspectraP <- NULL
meanspectraE <- NULL
meanspectraPCI <- array(0,c(2,300))
meanspectraECI <- array(0,c(2,300))

for (f in 1:300){

mbs <- amperrors(tempspectraP[,f],method='boot',quantiles=95,nresamples=nbootstraps)
meanspectraP[f] <- mbs$meanamp
meanspectraPCI[1,f] <- mbs$lowerCI
meanspectraPCI[2,f] <- mbs$upperCI

mbs <- amperrors(tempspectraE[,f],method='boot',quantiles=95,nresamples=nbootstraps)
meanspectraE[f] <- mbs$meanamp
meanspectraECI[1,f] <- mbs$lowerCI
meanspectraECI[2,f] <- mbs$upperCI

meanwavesP <- apply(tempwavesP,2,mean)
meanwavesE <- apply(tempwavesE,2,mean)
meanwavesPCI <- array(0,dim=c(2,length(meanwavesP)))
meanwavesECI <- array(0,dim=c(2,length(meanwavesE)))
nsubjs <- dim(tempwavesP)[1]
for (t in 1:length(meanwavesP)){
  bspop <- NULL
  for (s in 1:nbootstraps){bspop[s] <- mean(sample(tempwavesP[,t],nsubjs,replace=TRUE))}
  meanwavesPCI[,t] <- quantile(bspop,c(0.025,0.975))
}
for (t in 1:length(meanwavesE)){
  bspop <- NULL
  for (s in 1:nbootstraps){bspop[s] <- mean(sample(tempwavesE[,t],nsubjs,replace=TRUE))}
  meanwavesECI[,t] <- quantile(bspop,c(0.025,0.975))
}

@@

@@

plotlims <- c(12,40,0,0.03)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(19,0.03,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(14,0.028,'(c)',adj=0.5,cex=2.5)

@@

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(19,0.03,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(14,0.028,'(d)',adj=0.5,cex=2.5)

@@

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(19,0.03,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(14,0.028,'(e)',adj=0.5,cex=2.5)

@@

plotlims <- c(-1,13,-1,1) 
ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
ticklocsy <- seq(-1,1,1)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

# polygon(frequencies[c(11:51,51:11)],c(meanspectraPCI[1,11:51],meanspectraPCI[2,51:11]),col=colpal[2],border=NA)

lines(times, sinewave, col='black', lwd=3)

text(-0.7,0.88,'(a)',adj=0.5,cex=2.5)

@@

@@

```{r pupildata, fig.cap="Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation, with the driving signal plotted at the foot. Panel (b) shows the average Fourier spectrum. Panels (c,d) show contrast response functions at 2Hz for different conditions. Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped 95 percent confidence intervals.", fig.align="center", echo=FALSE}

@@

@@

plotlims <- c(12,40,0,0.8)  
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(19,0.8,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(14,0.75,'(f)',adj=0.5,cex=2.5)

@@

plotlims <- c(-1,13,-1,1) 
ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
ticklocsy <- seq(-1,1,1)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

>>>>

---
title: "Different rules for binocular combination of luminance in cortical and subcortical pathways"
author: "Federico G. Segala, Aurelio Bruno, Alex R. Wade &  Daniel H. Baker (+Myat? +Joel?)"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document: default
  pdf_document:
    toc: no
  html_document: default
bibliography: references.bib
csl: elife.csl
---

@@

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping and modelling
# 3 - download all raw data and analyse (requires XGB of storage)

# check which packages are installed, install the missing ones, and activate
packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'osfr','FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
rawdir <- 'local/rawdata/'
if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
figdir <- 'Figures/'
if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
datadir <- 'local/processeddata/'
if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data

@@

         # if the tar file of this participant's data doesn't exist
         if (!file.exists(paste0(rawdir,'P',100+participant,'.tar'))){
           # download it from OSF
           if (!exists('osffiles')){
           osfnode <- 'x8u4v'
           osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffiles$name==paste0('P',100+participant,'.tar'))
          osf_download(osffiles[fid,],rawdir,progress=TRUE)
         }

@@

for (participant in 1:30){
         # if the tar file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',100+participant,'summary.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '2qu6y'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',100+participant,'summary.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

          if (!file.exists(paste0(datadir,'headerfile.csv'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '2qu6y'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',100+participant,'headerfile.csv'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
          }

  hdata <- read.csv(paste0(datadir,'headerfile.csv'))

d <- dir(datadir,pattern='*summary.RData',full.names=TRUE)

@@

    temp <- tempmeansP[,cond,level]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansP[cond,level] <- mbs$meanamp
    cleanmeansPCI[1,cond,level] <- mbs$lowerCI
    cleanmeansPCI[2,cond,level] <- mbs$upperCI
    }

    temp <- tempmasksP[,cond,level]
    cartdata <- data.frame(Re(temp),Im(temp))
    if (sum(cartdata)!=0){
      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
      i <- which(D<SDthresh) 
          mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksP[cond,level] <- mbs$meanamp
    cleanmasksPCI[1,cond,level] <- mbs$lowerCI
    cleanmasksPCI[2,cond,level] <- mbs$upperCI
}

      temp <- apply(tempmeansE[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansEav[cond,level] <- mbs$meanamp
    cleanmeansEavCI[1,cond,level] <- mbs$lowerCI
    cleanmeansEavCI[2,cond,level] <- mbs$upperCI
      }

temp <- apply(tempmasksE[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksEav[cond,level] <- mbs$meanamp
    cleanmasksEavCI[1,cond,level] <- mbs$lowerCI
    cleanmasksEavCI[2,cond,level] <- mbs$upperCI
        }

temp <- apply(tempmeansE2[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE2av[cond,level] <- mbs$meanamp
    cleanmeansE2avCI[1,cond,level] <- mbs$lowerCI
    cleanmeansE2avCI[2,cond,level] <- mbs$upperCI
        }

      temp <- apply(tempmasksE2[,electrodeindices,cond,level],1,mean)
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE2av[cond,level] <- mbs$meanamp
    cleanmasksE2avCI[1,cond,level] <- mbs$lowerCI
    cleanmasksE2avCI[2,cond,level] <- mbs$upperCI
        }

@@

      temp <- tempmeansE[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE[ch,cond,level] <- mbs$meanamp
    cleanmeansECI[1,ch,cond,level] <- mbs$lowerCI
    cleanmeansECI[2,ch,cond,level] <- mbs$upperCI
}

      temp <- tempmasksE[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE[ch,cond,level] <- mbs$meanamp
    cleanmasksECI[1,ch,cond,level] <- mbs$lowerCI
    cleanmasksECI[2,ch,cond,level] <- mbs$upperCI
        }

      temp <- tempmeansE2[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmeansE2[ch,cond,level] <- mbs$meanamp
    cleanmeansE2CI[1,ch,cond,level] <- mbs$lowerCI
    cleanmeansE2CI[2,ch,cond,level] <- mbs$upperCI
        }

      temp <- tempmasksE2[,ch,cond,level]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
    cleanmasksE2[ch,cond,level] <- mbs$meanamp
    cleanmasksE2CI[1,ch,cond,level] <- mbs$lowerCI
    cleanmasksE2CI[2,ch,cond,level] <- mbs$upperCI
        }

@@

meanspectraP <- (1:300)*0
meanspectraE <- (1:300)*0
meanspectraPCI <- array(0,c(2,300))
meanspectraECI <- array(0,c(2,300))

for (f in 2:300){

        temp <- tempspectraP[,f]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
meanspectraP[f] <- mbs$meanamp
meanspectraPCI[1,f] <- mbs$lowerCI
meanspectraPCI[2,f] <- mbs$upperCI
      }

        temp <- tempspectraE[,f]
      cartdata <- data.frame(Re(temp),Im(temp))
      if (sum(cartdata)!=0){
        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
        i <- which(D<SDthresh) 
mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
meanspectraE[f] <- mbs$meanamp
meanspectraECI[1,f] <- mbs$lowerCI
meanspectraECI[2,f] <- mbs$upperCI
      }
}

meanwavesP <- NULL
meanwavesE <- NULL
meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))
meanwavesECI <- array(0,dim=c(2,dim(tempwavesE)[2]))
nsubjs <- dim(tempwavesP)[1]
for (t in 1:dim(tempwavesP)[2]){
  temp <- tempwavesP[,t]
  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
  meanwavesP[t] <- mean(temp[i])
  bspop <- NULL
  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
  meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
}

for (t in 1:dim(tempwavesE)[2]){
    temp <- tempwavesE[,t]
  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
  meanwavesE[t] <- mean(temp[i])
  bspop <- NULL
  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
  meanwavesECI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
}

@@

         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '2qu6y'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name=='Averagedata.RData')
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }

@@

plotlims <- c(15,40,0,0.03) 
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.03,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.028,'(c)',adj=0.5,cex=2.5)

@@

condlist <- c(1,5,6)
pointlist <- c(21,24,25)
for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
}  
legend(22,0.03,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.028,'(d)',adj=0.5,cex=2.5)

@@

for (cond in 4:6){
  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
}
legend(22,0.03,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.028,'(e)',adj=0.5,cex=2.5)

@@

plotlims <- c(-1,13,-1,0.5) 
ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

filt <- butter(3,0.083)
filtwaveP <- filter(filt, meanwavesP)
filtU <- filter(filt,meanwavesPCI[1,])
filtL <- filter(filt,meanwavesPCI[2,])
polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)

lines(times, filtwaveP, col=colpal[2], lwd=1.5)

lines(times, (sinewave/10)-0.9, col='black', lwd=3)

text(-0.7,0.4,'(a)',adj=0.5,cex=2.5)

@@

      for (n in 1:length(p5@paths)){
    temp <- class(p5@paths[n]$path)[1]
    if (pmatch(temp,"PictureFill",nomatch=0)){
      if (sum(col2rgb(p5@paths[n]$path@rgb))<765){p5@paths[n]$path@rgb <- addalpha(p5@paths[n]$path@rgb,alpha=0.2)}}}

@@

```{r pupildata, fig.cap="Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Panel (b) shows the average Fourier spectrum. Panels (c,d) show contrast response functions at 2Hz for different conditions. Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", echo=FALSE}

@@

hdata <- read.csv(paste0(datadir,'headerfile.csv'))

         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '2qu6y'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name=='Averagedata.RData')
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }

@@

plotlims <- c(15,40,0,0.8)  
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
legend(22,0.8,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.75,'(f)',adj=0.5,cex=2.5)

@@

plotlims <- c(-1,13,-10,20) 
ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
ticklocsy <- seq(-10,20,10)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks
